Universal Anonymous Signatures

### 2022-07-28 prism-backend/research/gsac/relationships.tex
Moved RAC to main body, and DAC to app. Sync'ed RAC with new syntax.

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Issuance functions:}
      \begin{align}
        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
        & \fissue^{single,F,I,L}(\upk,\cdot,\cdot) \coloneqq
          \pcif F(I||\upk) \in L~\pcreturn 0;~\pcelse \pcreturn F(I||\upk)
          \nonumber \\
        & \fissue^{\sring}(\upk,\attrs,\cdot) \coloneqq
          \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber \\
        & \fissue^{l,\dattrs}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
          \pcreturn (\attrs_1 = l+1 \land \attrs \subseteq
          \cup_{i\in\dattrs} \cattrs_i) \nonumber
      \end{align}

      \textbf{Signature evaluation functions:}
      \begin{align}
        & \feval^0(\cdot,\cdot,\cdot) \coloneqq \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs}(\cdot,(\cid,\attrs),\cdot)
          \coloneqq \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},\ast)
          \nonumber \\
        & \feval^{\sring,\dattrs}(\upk,(\cid,\attrs),\cdot)
          \coloneqq \pcif \upk \in \lbrace \attrs_i \rbrace_{i\in\dattrs}
          \subseteq \sring:
          \pcreturn (\lbrace \attrs_i \rbrace_{i\in\dattrs},\ast);
          \pcelse \pcreturn \bot \nonumber \\
        & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
          \pcreturn((\attrs_1,\lbrace\attrs_i\rbrace_{i\in\dattrs}),\ast)
          \nonumber
      \end{align}
    \end{minipage}
  }
  \vspace*{1em}

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Open functions:}
      \begin{align}
        & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
        & \finsp^{\upk}(\cdot,\upk,\cdot,\cdot) \coloneqq
          \pcreturn \upk % \CCommit(\usk;0)
          \nonumber
      \end{align}
    \end{minipage}
    \hspace*{5em}
    % \begin{minipage}[t]{0.47\textwidth}
    %   \begin{framed}
    %     $\attrs(\cred)$ returns all attributes in \cred \\
    %     $\dattrs(\cred)$ returns $\dattrs \subseteq \attrs(\cred)$ \\
    %     $\attrs_i(\cred)$ returns $i$-th attribute in \cred \\
    %     $\ast$ means the output is ignored \\
    %     $\bot$ means the function fails
    %   \end{framed}
    % \end{minipage}
  }
  \caption{Functions for the \CUASGen restrictions described next.
    For readability, we use ``$\cdot$'' to denote input arguments that are
    ignored; and ``$\ast$'' to denote output values that can be set to anything
    (but should be ignored). $\bot$ means the function fails.}
    % $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
    % $\dattrs \subseteq \attrs(\cred)$. $\attrs_i(\cred)$ returns $i$-th
    % attribute in \cred. $\ast$ means the output is ignored (in these examples,
    % we use this to mean that $\yeval^1$ is unused. $\bot$ means the function
    % fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

\subsubsection{\CUASGS construction.} %
We show that the $(\fissue^{single,L},\feval^0,\finsp^{\upk})$-\CUASGen
restriction, is a secure group signature scheme according to \cite{bsz05}.
Observe that the $\fissue^{single,F,I,L}$ function is further parameterized with
a list $L$ maintained by the issuer and must be fetched by users prior to
joining. It restricts that any user can have at most one credential (associated
to a same user key pair). We first quickly define the algorithms, and then
prove security.

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs the \Setup algorithm
  of \CUASGen, and one instance of \KeyGen and \ISet with
  $\fissue^{single,F,I,L}$ (both for the same user, who will be the only issuer
  in the GS scheme) and \OKeyGen. Assigns the public keys to \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \KeyGen from \CUASGen.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen,
  where $\yeval = 0$ is the constant output of $\feval^0$.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
  outputs.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
  0,\msg,\feval^0)$. Internally, the call to \Open runs $\finsp^{\upk}$.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
  0,\msg)$.
\end{description}

@@

We adopt the model in \cite{fhs19}, for anonymous credentials with selective
disclosure. Therein, an anonymous credential scheme is
defined via $OrgKeyGen$ (which we rename to $IssKeyGen$), and $UserKeyGen$
algorithms (roughly equivalent to
\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
interactive protocols. The issuance interactive protocol corresponds to
the issuance protocol in \UAS. Similarly, $Show,Verify$ corresponds to
the interactive extension of \Sign and \Verify in \UAS, which we show how
to build in \appref{app:interactive-uas}. The security definitions rely on
$HU, CU, ObtIss, Obtain, Issue,Show$, and $LoR$ oracles, which are essentially
equivalent to our \HUGEN, \CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb
oracles. We refer to \cite{fhs19} for the full details. For ease of reference,
we summarize the security definitions in \figref{fig:model-ac}.% , with inocuous
% adaptations to make them more suitable for comparison with our definitions --
% namely, we explicitly add a common setup process which is part of $IssKeyGen$
% in \cite{fhs19}.

@@

\subsection{Delegatable Anonymous Credentials}
\label{ssec:related-models-dac}

We give a simple definition for a Delegatable Anonymous Credentials (DAC)
scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
our simple scheme built from $\CUASGen^{usr-iss}$ does not ensure privacy of the
delegation chain -- which could be achieved by making \feval output projective
proofs like in \cite{bcc+09}, but since our goal is to showcase the feasibility
of building DAC from \UAS, we leave that out for brevity. Our simple scheme
does, however, ensure that a (not top-level) issuer can only delegate attributes
contained in a credential it owns. Also, for simplicity, we restrict to the case
of using one credential per signature/interactive credential presentation, and
assume that all parties use the same opener and \finsp function.
%
The functionality is thus defined almost as in \secref{ssec:related-models-ac},
i.e., we have $Setup$, $IssKeyGen$ algorithms, and $\langle Obtain,Issue\rangle$
and $\langle Show,Verify \rangle$ interactive protocols; but we do not have
$UserKeyGen$, as this collapses with $IssKeyGen$.
%
In the model for this setting, since there are multiple issuers, in addition
to the oracles in \secref{ssec:related-models-ac}, we use $HI$ and $CI$ oracles,
equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
issuers, and corrupt existing ones, respectively. The issuance and sign
anonymity properties are direct, constraining the adversary to output challenge
credentials and signatures with the same delegation chain. For unforgeability,
we still require that no adversary can authenticate using a set of attributes
that have not been issued to a corrupt user. In addition, we require that for
any successful authentication using a level-$l$ credential, we
can extract a chain of credentials of length $l$ such that each level-$i$
credential can be used successfully to authenticate a level-$(i+1)$ credential
down to the level-$l$ credential, and the attributes revealed in the
level-$l$ authentication are contained in all the credentials up the chain.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}
      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
        \pccomment{Abort if challenge creds belong to} \\
        \pccomment{users with different delegation chains} \\
        \pcreturn b^*
      }
      \vspace*{0.5em}

      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
        \pccomment{Abort if challenge sigs belong to} \\
        \pccomment{users with different delegation chains} \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (D=(l,D'),\ipk_l,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm) \\
        \langle\cdot,(b,\utrans)\rangle \gets
        \langle \adv(\st),\Verify(\ipk_l,D)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,l]})
        \gets ExtractChain(\utrans) \\ 
        \pcif \exists i \in [1,l]~\suchthat~
        \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
        \pcind D' \not\subseteq \ATTR[\iid]) \land
        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for delegatable anonymous credentials with selective
    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HI,
    CI,Obtain,Issue,ObtIss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon} \gets
    \lbrace HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$. $\mathcal{O}_{forge}
    \gets \lbrace HI,CI,Obtain,ObtIss,Issue,Show\rbrace$. $IssLor$ corresponds
    to \OBTCHALb in \UAS, whereas $SigLor$ corresponds to \CHALb. Also, \OWNR
    and \ATTR tables are essentially as in \secref{ssec:model-uas}.
    $\ISR[\ipk]$, in this case, returns the identifier of the issuer with public
    key \ipk. With $D = (l,D')$ we mean that the first attribute in the revealed
    set $D$ is $l$, which denotes the level of the credential used for
    authentication.}
  \label{fig:model-dac}  
\end{figure}

\subsubsection{\CUASDAC Construction.} %
We next give a construction of a delegatable AC (DAC) scheme, in the shape of
a $(\fissue^{l,\dattrs},\feval^{l,\dattrs},\finsp^0)$-$\CUASGen^{usr-iss}$
restriction. In a DAC scheme, all users are (or may be) also issuers. We only
distinguish between top-level issuers, who have level $l=0$, and lower-level
issuers, who have level $l>0$. In our \CUASDAC scheme, we assume that the first
attribute (after the user's secret key) encodes the level of the credential.
That is, $\attrs_1=l$, for a credential of level $l$. In addition, all users
(i.e., with $l>0$) who want to delegate have to publicly list:

\begin{enumerate}
\item The level $l$ of the credential they delegate.
\item Their public key \ipk.
\item An \UAS signature proving knowledge of a credential of level $l$, and over
  the attributes that this level-$l$ issuer is delegating.
\item The \ipk of the parent issuer.
\item The $\fissue^{l,\dattrs}$ function they will require for delegating.
\item An $\feval^{l,\dattrs}$ function used to produce the signature at item 3.
\end{enumerate}

We assume that, from an \ipk, it is possible to find the corresponding issuer
(e.g., using the previously mentioned public list). The mentioned
$\fissue^{l,\dattrs}$ functions must follow the pattern in \figref{fig:func-restrictions}.
Namely, the issuance function checks that the first requested attribute equals
$l+1$, and that all requested attributes are a subset of the attribute set
\dattrs being delegated by the level-$l$ issuer. In addition, signature
evaluation functions $\feval^{l,\dattrs}$, also shown in \figref{fig:func-restrictions},
must reveal the level of the credential used to produce the \UAS signature at
item 2, as well as the set of attributes \dattrs that the level-$l$ issuer
delegates. Verifiers can then trivially check if the set of revealed attributes
are contained within the attributes delegatable by the parent issuer%
\footnote{Additional checks may be added in both functions, but this is
  the bare minimum.}.
%
From this high-level description, we define the algorithms of \CUASDAC:

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
  and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
  $\CUASGen^{usr-iss}$ construction. Returns $\parm \gets (\parm',\opk)$. Note
  that $\finsp^0$ can be replaced by any desired opening function.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $l=0$, simply run \IKeyGen as
  in $\CUASGen^{usr-iss}$. If $l>0$, this level-$l$ issuer picks a random
  message $r$ and computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
  \feval^{l,\dattrs})$, for the \dattrs set it wants to reveal -- which must
  include the attributes to delegate, and the credential level. It then
  publishes $(l,\ipk,\Sig,\ipk^{l-1},\fissue^{l,\dattrs},\feval^{l,\dattrs})$,
  where $\ipk^{l-1}$ is the public key of the parent issuer,
  $\fissue^{l,\dattrs}$ is an issuance function as described in
  \figref{fig:func-restrictions}, and $\feval^{l,\dattrs}$ is also as in
  \figref{fig:func-restrictions}, revealing the attributes that the issuer is
  willing to delegate.
% \item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
%   also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
%   $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
%   credentials. Note that this does not affect security, as long as
%   $\isk \getr \AttrSpace$.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  If $l>0$, the user first finds the corresponding $(l,\ipk,\Sig,\ipk^{n-1},
  \fissue^{l,\dattrs},\feval^{l,\dattrs})$ tuple, and checks \Sig running
  \Verify as in $\CUASGen^{usr-iss}$ (with the retrieved $\feval^{l,\dattrs}$).
  Then, user and level-$l$ issuer run $\langle\Obtain,\Issue\rangle$ as in
  $\CUASGen^{usr-iss}$, using $\fissue^{l,\dattrs}$ as issuance function. If
  $l=0$, then both run $\langle\Obtain,\Issue\rangle$ as in
  $\CUASGen^{usr-iss}$, using the \fissue function required by the issuer.
\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle
  \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of
  $\CUASGen^{usr-iss}$.  
\end{description}

\paragraph{Security of \CUASDAC.} %
We state next the theorems for the security of \CUASDAC. The proofs are
available in \appref{app:related-proofs}.

\begin{theorem}[Issuance anonymity of \CUASDAC]
  If the base \CUASGen construction has issuance anonymity according to
  \defref{def:issue-anonymity-uas}, then \CUASDAC also has issuance anonymity.
\end{theorem}

\begin{theorem}[Signature anonymity of \CUASDAC]
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, then \CUASDAC also has signature anonymity.
\end{theorem}

\begin{theorem}[Unforgeability of \CUASAC]
  If the base \CUASGen construction has issuance and signature unforgeability
  according to \defref{def:issue-forge-uas} and \defref{def:sign-forge-uas}, and
  non-frameability according to \defref{def:frame-uas}, then \CUASAC is an
  unforgeable AC scheme.
\end{theorem}

>>>>

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Issuance functions:}
      \begin{align}
        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
        & \fissue^{single,F,I,L}(\upk,\cdot,\cdot) \coloneqq
          \pcif F(I,\upk) \in L~\pcreturn 0;~\pcelse \pcreturn F(I,\upk)
          \nonumber \\
        & \fissue^{\sring}(\upk,\attrs,\cdot) \coloneqq
          \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber
      \end{align}

      \textbf{Signature evaluation functions:}
      \begin{align}
        & \feval^0(\cdot,\cdot,\cdot) \coloneqq \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs}(\cdot,(\cdot,\attrs),\cdot)
          \coloneqq \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},\ast)
          \nonumber \\
        & \feval^{\sring,\dattrs}(\upk,(\cdot,\attrs),\cdot)
          \coloneqq \pcif \upk \in \lbrace \attrs_i \rbrace_{i\in\dattrs}
          \subseteq \sring:
          \pcreturn (\lbrace \attrs_i \rbrace_{i\in\dattrs},\ast);
          \pcelse \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs,F,V,L}(\upk,((\cidi,\cidu),\attrs),\cdot) \coloneqq
          \nonumber \\
        & \hspace*{2em}\pcif F(V,\cidi) \in L \lor F(V,\cidu) \in L:
          \pcreturn (0,\ast) \nonumber \\
        & \hspace*{2em}\pcelse \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},V)
        \nonumber   
      \end{align}
    \end{minipage}
  }
  \vspace*{1em}

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Open functions:}
      \begin{align}
        & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
        & \finsp^{\upk}(\cdot,\upk,\cdot,\cdot) \coloneqq
          \pcreturn \upk % \CCommit(\usk;0)
          \nonumber \\
        & \finsp^{F}((\yeval^0,\yeval^1),\cdot,((\cidi,\cidu),\attrs),\cdot)
          \coloneqq \nonumber \\
        & \hspace*{2em}\pcif \yeval^0 \neq 0:
          \pcreturn (F(\yeval^1,\cidi),F(\yeval^1,\cidu)) \nonumber \\
        & \hspace*{2em}\pcelse \pcreturn 0
          \nonumber
      \end{align}
    \end{minipage}
    \hspace*{5em}
    % \begin{minipage}[t]{0.47\textwidth}
    %   \begin{framed}
    %     $\attrs(\cred)$ returns all attributes in \cred \\
    %     $\dattrs(\cred)$ returns $\dattrs \subseteq \attrs(\cred)$ \\
    %     $\attrs_i(\cred)$ returns $i$-th attribute in \cred \\
    %     $\ast$ means the output is ignored \\
    %     $\bot$ means the function fails
    %   \end{framed}
    % \end{minipage}
  }
  \caption{Functions for the \CUASGen restrictions described next.
    For readability, we use ``$\cdot$'' to denote input arguments that are
    ignored; and ``$\ast$'' to denote output values that can be set to anything
    (but should be ignored).}
    % $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
    % $\dattrs \subseteq \attrs(\cred)$. $\attrs_i(\cred)$ returns $i$-th
    % attribute in \cred. $\ast$ means the output is ignored (in these examples,
    % we use this to mean that $\yeval^1$ is unused. $\bot$ means the function
    % fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

\subsubsection{\CUASGS construction.} %
We show that the $(\fissue^{single,F,IL},\feval^0,\finsp^{\upk})$-\CUASGen
restriction, is a secure group signature scheme according to \cite{bsz05}.
Observe that the $\fissue^{single,F,I,L}$ function is further parameterized with
a list $L$ maintained by the issuer and must be fetched by users prior to
joining. It restricts that any user can have at most one credential (associated
to a same user key pair). We first quickly define the algorithms, and then
prove security.

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs \Setup from \CUASGen,
  and one instance of \KeyGen and \ISet with $\fissue^{single,F,I,L}$ (both for
  the same user, who will be the only issuer in the GS scheme) and \OKeyGen.
  Assigns the public keys to \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \KeyGen from \CUASGen.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. If the issuer
  gets $\yissue = 0$, rejects issuing a new credential. Otherwise, it completes
  the protocol and adds $\yissue$ to $L$.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen,
  where $\yeval = 0$ is the constant output of $\feval^0$.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
  outputs.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
  0,\msg,\feval^0)$. Internally, the call to \Open runs $\finsp^{\upk}$.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
  0,\msg)$.
\end{description}

@@

We adopt the model in \cite{fhs19}, for anonymous credentials with selective
disclosure. Therein, an anonymous credential scheme is defined via $OrgKeyGen$
(which we rename to $IssKeyGen$, and is equivalent to \KeyGen+\ISet in \UAS),
and $UserKeyGen$ (\KeyGen in \UAS) algorithms, and $Obtain,Issue$ and $Show,
Verify$ interactive protocols. The issuance interactive protocol corresponds to
the issuance protocol in \UAS. Similarly, $Show,Verify$ corresponds to
the interactive extension of \Sign and \Verify in \UAS, which we show how
to build in \appref{app:interactive-uas}. The security definitions rely on
$HU, CU, ObtIss, Obtain, Issue, Show$, and $LoR$ oracles, which are essentially
equivalent to our \UGEN, \UCORR, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb
oracles\footnote{The $CU$ oracle in \cite{fhs19} actually allows the adversary
  to create corrupt user secret keys, while in our corruption model, corrupt
  users have keys generated by the system that are later learned by the
  adversary. This is however for notational simplicity -- and, indeed, in our
  construction, all users need to prove knowledge of the \usk, which would be
  consistent with the stronger corruption model in \cite{fhs19}}. We refer to
\cite{fhs19} for the full details. For ease of reference, we summarize the
security definitions in \figref{fig:model-ac}.% , with inocuous
% adaptations to make them more suitable for comparison with our definitions --
% namely, we explicitly add a common setup process which is part of $IssKeyGen$
% in \cite{fhs19}.

@@

\subsection{Revocable Anonymous Credentials}
\label{sapp:related-models-rac}

In \cite{cks10}, revocable anonymous credentials are proposed. From \CUASGen, it
is straightforward to build an AC system with verifier local revocation, like in
\cite{bs04}. Basically, we leverage the $\cid=(\cidi,\cidu)$ identifiers,
encoded as attributes, to define a $(\feval,\finsp)$ function pair that: (1)
ensures that opening outputs a one-way function of the {\cid}s concatenated with
the verifier name; and (2) ensures that, if the {\cid}s have been added to a
revocation list by the verifier, the verifier will know it -- and hence will be
able to reject the signature. We first give a simple model in
\figref{fig:model-rac}, extending that in \secref{ssec:related-models-ac}.
Concretely, to the functionality in \secref{ssec:related-models-ac}, we now
explicitly add
the $OKeyGen$ function (equivalent to \OKeyGen, with a fixed \finsp function),
which generates the opener key pair, extend $Verify$ to receive also a list $L$
of revoked identifiers, and we add a function (and corresponding oracle) $id/\bot
\gets RetrieveCredId(\osk,\utrans)$ that can extract the identifier of the
credential used in a presentation transcript \utrans -- and which is essentially
equivalent to \Open in \UAS. For simplicity, we do not include the equivalent to
verifiable openings, but this would be straightforward.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        b^* \gets \adv^{\mathcal{O}_{anon}}(\parm,\ipk,\opk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\
        (D,L,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm,\ipk) \\
        \langle \cdot,(b,\utrans)\rangle
        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\    
        h \gets RetrieveCredHandle(\osk,\utrans) \\
        \pcif h \in L \lor h = \bot: \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for revocable anonymous credentials with selective
    disclosure based on \cite{fhs19}. 
    $\mathcal{O}_{anon} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
    ReqCredHandle,LoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace HU,CU,
    Obtain,ObtIss,Issue,Show,ReqCredHandle \rbrace$. $ReqCredHandle$ is
    equivalent to \OPEN, operating on transcripts \utrans instead of signatures.
    Also, \OWNR and \ATTR tables are essentially as in \secref{ssec:model-uas}.}
  \label{fig:model-rac}  
\end{figure}

\subsubsection{\CUASRAC Construction.} %
Briefly, we build a revocable anonymous credential as a $(\fissue^1,
\feval^{\dattrs,F,V,L},\finsp^{F})$-\CUASGen restriction. The \feval is
parameterized with a one-way and collision-resistant function $F$
(e.g., a cryptographic hash), a string identifying the verifier $V$ and a
list $L$ of ``revocation handles'' by $V$. 
%
Since credentials in \CUASGen have two identifiers (\cidi, chosen by the issuer;
and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally computes
$F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval sets $\yeval^0$
to $0$, which the verifier interprets as ``revoked credential''. Otherwise,
it sets $\yeval^0 \gets \dattrs(\cred)$ and $\yeval^1 \gets V$; $\yeval^1$ is
then used by $\finsp^F$ to compute $\yinsp \gets (F(\yeval^1,\cidi),
F(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
%
In more detail, the algorithms are as follows:

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
  \CUASGen.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
  \CUASGen construction, setting $\finsp^F$ as opening function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from the
  \CUASGen construction.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
  \attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
  $\finsp^F$ as open function.
\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
  Gets $(\sig,\yeval)$ from the $\langle Show,\Verify\rangle$ transcript
  \utrans, and runs \Open from \CUASGen. If $\yeval^0 \neq 0$ (i.e., the
  signature was created by a non-revoked credential), this returns $(F(V,\cidi),
  F(V,\cidu))$, which the verifier can add to its revocation list $L$.
\end{description}

\paragraph{Security of \CUASRAC.} %
We state next the theorems for the security of \CUASRAC. The proofs are
available in \appref{app:related-proofs}.

\begin{theorem}[Issuance anonymity of \CUASRAC]
  \todo{review}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, and $F$ is one-way and collision-resistant,
  then \CUASAC is an anonymous AC scheme according to \cite{fhs19}.  
\end{theorem}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base \CUASGen construction has sign unforgeability according to
  \defref{def:sign-forge-uas}, and $F$ is one-way and collision-resistant, then
  \CUASRAC is an unforgeable RAC scheme.
\end{theorem}
